Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-03-10 eg6-letters/incoherent/responsereferee.tex

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Summary of Changes}
Below is a summary list of the changes to the paper and their location in the text.  The following sections contain responses to the referees, where we feel we have largely addressed the expressed concerns.  Note, we would like to refute the claims regarding the invalidity of the $Q^2$ selection and factorization assumptions, particularly regarding this letter's relationship to a large history of published research in this field.

\begin{itemize}
    \item{The title and abstract were completely rewritten.}
    \item{The summary was updated with future plans inclluding an upcoming experiment.}
    \item{Removed some unnecesary experimental details that are standard to CLAS analyses, and added a corresponding reference, in the right column of page 3.}
    \item{Added a sentence on the relationship between the GPD $H$ and PDFs, after equation 5.}
    \item{Explicitly mentioned the standard nature and justification of the $Q^2>2$ GeV selection, at the beginning of page 4.}
    \item{Motivation for the $t>t_{min}$ selection was clarified, in the left coulmn of page 4.}
    \item{Treatment of $\pi^0$ contamination and subtraction was clarified, in the paragraph starting at the end of page 4.}
    \item{The dominance of $a_0$, the Compton Form Factor, and the GPD $H$, was clarified and supported with references, in the left column of page 5.}
    \item{Minor grammar and style updates.}
\end{itemize}

### 2019-03-10 eg6-letters/incoherent/responsereferee.tex

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Summary of Changes}
Below is a summary list of the changes to the paper and their location in the text.  The following sections contain responses to the referees, where we feel we have addressed the expressed concerns.  Note, we would like to refute the claims regarding the invalidity of the $Q^2$ selection and factorization assumptions, particularly regarding this letter's relationship to a large history of published research in this field.

\begin{itemize}
    \item{The title and abstract were completely rewritten.}
    \item{The summary was updated with future plans including an upcoming experiment.}
    \item{Removed some unnecessary experimental details that are standard to CLAS analyses, and added a corresponding reference, in the right column of page 3.}
    \item{Added a sentence on the relationship between the GPD $H$ and PDFs, after equation 5.}
    \item{Explicitly mentioned the standard nature and justification of the $Q^2>2$ GeV selection, at the beginning of page 4.}
    \item{Motivation for the $t>t_{min}$ selection was clarified, in the left column of page 4.}
    \item{Treatment of $\pi^0$ contamination and subtraction was clarified, in the paragraph starting at the end of page 4.}
    \item{The dominance of $a_0$, the Compton Form Factor, and the GPD $H$, was clarified and supported with references, in the left column of page 5.}
    \item{Minor grammar and style updates.}
\end{itemize}

@@

The authors assume a factorization of their measured process as a DVCS process on a single quasi-free proton and a nuclear spectral function, and then compare with an inclusive EMC effect and with a QMC calculation, and conclude that they find medium-modified GPDs beyond these. But there is no one-to-one comparison possible, as the nuclear ratio they measure is (at best!) a convolution of electron-quark scattering with the handbag mechanism, embedded in a nuclear medium, at $Q^2 > 1 $ GeV$^2$. It is certainly not a given that this at these scales is separable in a quasi-free DVCS-like process convoluted with a nuclear spectral function. The conclusion that the measured BSA is quenched and that nuclear effects exist is fair, but to link those at such low-$Q^2$ scales to possible medium modifications of the bound-proton’s partonic structure or, separately, to a new avenue to explore the origin of the EMC effect is a stretch. It reminds of initial $(e,e’p)$ experiments where quenching was also postulated to be related to bound-nucleon EMC-like effects. It is just too early to draw such conclusions, even more if it is not clear if one can interpret the data in this low-$Q^2$ region with a leading-twist handbag mechanism, and if this changes in the nuclear medium.}

\noindent \\
Answer:

We clarified the letter to make it clearer to the general reader where it is possible without adding too much material. Particularly, the physics behind the H GPD is clarified, the reasoning behind the minimum t cut, as well as the $\pi^0$ contamination and how we accounted for it (i.e. it is measured and subtracted at each kinematic). It is unclear what the referee is pointing at when mentioning that we assume impulse approximation for our conclusion. We do not draw any strong conclusion in favor of a particular interpretation of the result, beyond the fact that the result is at odds with existing models. Actually, as would be expected from any surprising first measurement, we point that this result should lead to further exploration of the question both on the theoretical and experimental levels.

We strongly disagree with the suggestion that the cut $Q^2 > 1$ GeV$^2$ is unjustified and improper. While some of the criticisms raised by the referee are sound, they may be forgetting that a significant aspect of this work involves comparing our results to previous experimental DVCS results from the past decade. Those results have systematically used such a cut, and a different choice for us would defeat the purpose of our comparison. Moreover, this cut is widely used in previously published results cited in the letter that are all consistent with the handbag diagram description: PRL 87, 182001; 97, 072002; 100, 162002; 114, 032001; 115, 212003; 119, 202004 just to quote PRL references. Such extended literature strongly establish this cut as the standard of the field, we fail to see how this letter could possibly be a reasonable place to revisit this standard.

### 2019-03-11 eg6-letters/incoherent/incoherent_prl.tex
*final* comments from Stepan

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state using the standard particle identification 
framework of the CLAS event reconstruction (see \cite{Hattawy:thesis} for 
additional details on the particle identification). Note that even though the 
DVCS reaction has only one real photon in the final state, events with more 
than one photon were not discarded at this stage. These extra photons were 
mostly soft photons from accidental coincidence which, as will be discussed 
below, the DVCS exclusivity cuts easily eliminated.  In the following selection 
stage, the most energetic photon was considered as the DVCS photon candidate.

@@

In the final sample, the exclusivity of the incoherent DVCS events was ensured 
by imposing a series of constraints based on the four-momentum conservation in 
the reaction $ep\rightarrow e'p'\gamma$.  These kinematical variables are: the 
coplanarity angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and 
($\gamma^*$,$p'$) planes, the missing energy, mass, and transverse momentum of 
the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass squared of the $e'p'$ 
system, and the angle $\theta$ between the measured photon and the missing 
momentum of the $e'p'$ system. The experimental data for the most relevant 
exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.

>>>>

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state using the standard particle identification 
framework of the CLAS event reconstruction (see \cite{Hattawy:thesis} for 
additional details on the particle identification). Note that even though the 
DVCS reaction has only one real photon in the final state, events with more 
than one photon were not discarded at this stage. These extra photons were 
mostly soft photons from accidental coincidence which, as will be discussed 
below, the DVCS exclusivity cuts easily eliminated.  In the following 
stage, the most energetic photon was considered as the DVCS photon candidate.

@@

In the final sample, the exclusivity of the incoherent DVCS events was ensured 
by imposing a series of constraints based on the four-momentum conservation in 
the reaction $ep\rightarrow e'p'\gamma$.  These kinematical variables are: the 
coplanarity angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and 
($\gamma^*$,$p'$) planes, the missing energy, mass, and transverse momentum of 
the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass squared of the $e'p'$ 
system, and the angle $\theta$ between the measured photon and the missing 
momentum of the $e'p'$ system. The experimental distributions for the most relevant 
exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
Fermi motion of the nucleons in the helium nucleus, the cuts indicated by the dashed lines
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.
